WSSSPE4-paper-reviewer-response

### 2017-12-18 WSSSPE4_report/WSSSPE4_paper.tex
changing slack section to subsection reducing details about survey mechanisms matching comments in response letter

This paper is a summary of a longer report~\cite{WSSSPE4-report} on the workshop and the submitted materials.
The remainder of the paper includes the call for papers (\S\ref{sec:preworkshop}); the WSSSPE Code of Conduct (\S\ref{sec:CoC}) and mission and vision (\S\ref{sec:mission}); a set of presentations that included a keynote, papers, lighting talks, and a panel (\S\ref{sec:presentations}); and the activities of a set of working groups (\S\ref{sec:WGs}).  One full day of the
workshop was spent with participants in the working groups, which occurred in parallel
with each other.  And each of the working groups left with a plan for how they could move
forward.
This report also mentions the Slack channel created for further discussions (\S\ref{sec:slack}), and it highlights an attendee survey (\S\ref{sec:survey}) before concluding (\S\ref{sec:conclusions}).
%An appendix lists the organizers and program committee members (\S\ref{sec:orgcom}).

@@

The CoC was discussed at the beginning of WSSSPE4, with the CoC subcommittee
and a general email address for reporting concerns or incidents, or
asking questions.  One concern was raised after the first half day, 
% regarding how part of the workshop was being run, 
and we changed the workshop
to address this.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Slack team and channels}\label{sec:slack}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As part of the discussion at WSSSPE4, we created a Slack team for WSSSPE~\cite{WSSSPESlack}.  To join it, go to \url{https://wssspe.signup.team/}.  A number of the working groups also created channels within the team; see the subsections in \S\ref{sec:WGs} for the names of these channels.

@@

All participants present on the last day of the meeting, 14 September 2016, were asked to complete the online survey administered through Qualtrics\footnote{\url{https://www.qualtrics.com}.}.
44 responses were recorded, with one respondent indicating that they took the survey twice.
The survey URL was also later distributed to attendees by email and advertised on twitter for attendees who were not there on the last day to have a chance to respond, and one additional response was recorded after the meeting.
Hence, the total number of unique individuals responding to the survey is likely 44.
The survey contained nine multiple choice and open-text answer questions.
Text responses have been alphabetized to preserve anonymity.
The survey had a 100\% completion rate.

In general, the respondents were highly satisfied with the meeting and interested in continuing and participating in WSSSPE activities.
The mix of topics and types of interactions---talks, panels and discussion---was well balanced with several indicating a desire for time for questions and answers following talks as well for discussions in general.
Many respondents indicated that they will remain engaged in WSSSPE working group initiatives.
However, demand for a professional organization encompassing WSSSPE interests was weaker with over half interested in joining and a large percentage willing to consider the idea.
Respondents were grateful for the opportunity to network, explore new collaborations and for travel support to the conference.

The survey results indicate that future WSSSPE conferences should consider the balance of the attendees.
This year's meeting had many first time and early career participants who would have benefited from a review of basic concepts and terminology including what it means for software to be sustainable and the roles of research software engineers.
Additional emphasis and topics to explore would be the inclusion of more case studies, focus on the decision making process in developing and using software, deeper dives into selected topics, tutorials, software training within and outside of STEM, lowering the barriers to implementing best practices in software development, and progress towards executing WSSSPE's vision.

>>>>

This paper is a summary of a longer report~\cite{WSSSPE4-report} on the workshop and the submitted materials.
The remainder of the paper includes the call for papers (\S\ref{sec:preworkshop}); the WSSSPE Code of Conduct (\S\ref{sec:CoC}) and mission and vision (\S\ref{sec:mission}); a set of presentations that included a keynote, papers, lighting talks, and a panel (\S\ref{sec:presentations}); and the activities of a set of working groups (\S\ref{sec:WGs}).  One full day of the
workshop was spent with participants in the working groups, which occurred in parallel
with each other.  And each of the working groups left with a plan for how they could move
forward.
This report also highlights an attendee survey (\S\ref{sec:survey}) before concluding (\S\ref{sec:conclusions}).
%An appendix lists the organizers and program committee members (\S\ref{sec:orgcom}).

@@

The CoC was discussed at the beginning of WSSSPE4, with the CoC subcommittee
and a general email address for reporting concerns or incidents, or
asking questions.  One concern was raised after the first half day, 
% regarding how part of the workshop was being run, 
and we changed the workshop
to address this concern.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Slack team and channels}\label{sec:slack}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As part of the discussion at WSSSPE4, we created a Slack team for WSSSPE~\cite{WSSSPESlack}.  To join it, go to \url{https://wssspe.signup.team/}.  A number of the working groups also created channels within the team; see the other subsections in \S\ref{sec:WGs} for the names of these channels.

@@

At the end of WSSSPE4, all remaining participants completed an on-line survey.
%
%All participants present on the last day of the meeting, 14 September 2016, were asked to complete the online survey administered through Qualtrics\footnote{\url{https://www.qualtrics.com}.}.
%44 responses were recorded, with one respondent indicating that they took the survey twice.
%The survey URL was also later distributed to attendees by email and advertised on twitter for attendees who were not there on the last day to have a chance to respond, and one additional response was recorded after the meeting.
%Hence, the total number of unique individuals responding to the survey is likely 44.
%The survey contained nine multiple choice and open-text answer questions.
%Text responses have been alphabetized to preserve anonymity.
%The survey had a 100\% completion rate.
%
In general, the respondents were highly satisfied with the meeting and interested in continuing and participating in WSSSPE activities.
The mix of topics and types of interactions---talks, panels and discussion---was well balanced with several indicating a desire for time for questions and answers following talks as well for discussions in general.
Many respondents indicated that they will remain engaged in WSSSPE working group initiatives.
There was weaker demand for a professional organization encompassing WSSSPE interests, with over half interested in joining and a large percentage willing to consider the idea.
Respondents were grateful for the opportunity to network, explore new collaborations and for travel support to the conference.

The survey results indicate that future WSSSPE conferences should consider the balance of the attendees.
WSSSPE4 had many first time and early career participants who would have benefited from a review of basic concepts and terminology including what it means for software to be sustainable and the roles of research software engineers.
Additional emphasis and topics to explore would be the inclusion of more case studies, focus on the decision making process in developing and using software, deeper dives into selected topics, tutorials, software training within and outside of STEM, lowering the barriers to implementing best practices in software development, and progress towards executing WSSSPE's vision.

### 2017-12-18 WSSSPE4_report/jors-response.tex
changing slack section to subsection reducing details about survey mechanisms matching comments in response letter

Nonetheless, we agree with the reviewers that this can be reduced, and have done so by removing the appendix and as advised by the reviewers, as further discussed below.  The revised version we are resubmitting has been reduced to 1 title page, \textcolor{red}{10} pages of body, and 3 pages of references, a reduction of \textcolor{red}{5} of the original 18 pages.

\textcolor{red}{Can we remove 2 more pages?}

@@

\textcolor{red}{NEED TO RESPOND}

@@

Similarly, while the code of conduct is provided in full, no context is provided for establishing a code of conduct for such an event. Why do events such as this benefit from a code of conduct? What is the social context in which codes of conduct in these types of events become established? In what ways does a code of conduct benefit this event? Instead of discussing these more general issues (maybe only some of them are needed here) an enigmatic comment about an event that required some form of intervention from the organizers is mentioned, but left unexplained. Would reporting more fully about what happened be beneficial to the reader?s understanding of the workshop? If not, maybe shortening this section would be better?

@@

@@

@@

3. In section 7: ``Text responses have been alphabetize'' => ``Text responses have been alphabetized''.
\end{quoting}

We have made these three requested changes.

%\printbibliography

>>>>

Nonetheless, we agree with the reviewers that this can be reduced, and have done so by removing the appendix and as advised by the reviewers, as further discussed below.  The revised version we are resubmitting has been reduced to 1 title page, \textcolor{red}{9.5} pages of body, and 3 pages of references, a reduction of \textcolor{red}{5.5} of the original 18 pages.

\textcolor{red}{Can we remove 1.5 more pages?}

@@

A paragraph in the survey section (7) has been removed.

@@

\end{quoting}
We've removed the discussion about the survey respondents and rate, etc.

While we agree that the reviewer has stated a workshop goal of improving research software, this is not something that we intended to do during the workshop itself, so we cannot measure how it has changed over the 2 1/2 days of the workshop.  We are trying to change the course of the community by pushing on the wheel of the ship, and it will take time to see how the ship responds.
\begin{quoting}

Similarly, while the code of conduct is provided in full, no context is provided for establishing a code of conduct for such an event. Why do events such as this benefit from a code of conduct? What is the social context in which codes of conduct in these types of events become established? In what ways does a code of conduct benefit this event?

\end{quoting}
We've removed the Code of Conduct itself.

We feel that many events in current society (see the \#metoo movement for example, or one of many discussions about the behavior of scientists at field sites) show how what many might think are common sense rules of conduct are not actually commonly followed.  At least anecdotally, and clearly in today's society, stating these rules makes in difference in behavior, and makes clear what is unacceptable.
\begin{quoting}

Instead of discussing these more general issues (maybe only some of them are needed here) an enigmatic comment about an event that required some form of intervention from the organizers is mentioned, but left unexplained. Would reporting more fully about what happened be beneficial to the reader's understanding of the workshop? If not, maybe shortening this section would be better?

We don't think that reporting on a specific incident is proper.

@@

\textcolor{red}{This paragraph is the main thing that has not been addressed yet. (Note that what the reviewer calls 4 and 5 are now 5 and 6.)}

@@

We dropped ``into''.

@@

We removed the detail about the survey, and initially mention the 68 workshop participants.

3. In section 7: ``Text responses have been alphabetize'' => ``Text responses have been alphabetized''.

We've made this change.
